Distributional Regression Forests for Probabilistic Precipitation Forecasting in Complex Terrain

### 2019-02-08 pkg/disttree/inst/draft/rejoinder2.Rnw
adapted response to Reviewer 1
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2456 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 314499749df9878932fd123c778d122447e73e95

Thank you very much for the positive and constructive feedback from you, 
the associate editor, and the two referees. Based on your comments, the
manuscript has been revised. In particular, an additional subsection
has been added to the discussion commenting on the complexity of the
applied distributions.
%The most important changes are:
%\begin{itemize}
%\item \emph{Discussion.}\\
%\item \emph{\ldots}\\
%\end{itemize}
All changes and extensions are explained in much more detail in the
point-to-point reply on the next pages.

@@

The missing information and reference have been added in the 
manuscript in Section~3.2 \textit{Models and evaluation: Distributional forest}.
The described parameters pertain to the forest-building
function \code{distforest}. But you are right, within the function \code{distforest} 
the arguments \code{minsplit}, \code{minbucket} and \code{alpha} are handed over to the 
tree-building function \code{disttree} which in this case applies the function \code{ctree}.

@@

Thank you for pointing this out. We have rephrased this sentence in Section 3.3. of the manuscript.

@@

Depending on the whether a maximum or a quadratic form of the test statistic is considered
for the standardized test statistic its asymptotic conditional distribution is either a 
normal ($c_{max}$) or a $\chi^2$ distribution ($c_{quad}$). 
We have added this information to the addressed section of Appendix~A.

>>>>

Thank you very much for the positive and constructive feedback from you, 
the associate editor, and the two referees. We have incorporated all
the remaining comments and, in particular, added a new subsection
discussing more complex distributions with non-orthogonal parameters.
All changes are explained in more detail in the point-to-point reply
on the next pages.

@@

We now point out that the arguments pertain to our function \code{distforest}
and include a forward reference to the ``computational details''.

You are also correct, though, that \code{ctree} takes these arguments. Internally,
\code{distforest}/\code{disttree} pass the arguments on to \code{cforest}/\code{ctree}.
This is now pointed out more clearly in the ``computational details''.

@@

We have rephrased this sentence, emphasizing that the \emph{forecasted} distributions
are depicted and avoiding an assessment.

@@

Depending on whether a maximum or a quadratic form of the test statistic is considered,
the asymptotic conditional distribution is either normal ($c_{max}$) or $\chi^2$ ($c_{quad}$). 
We have added this information in Appendix~A.
